Mergeable Types

### 2017-02-27 paper/dali.tex
Semantics.
edits

  In this paper, we present a new interpretation of replicated types
  that overcome these concerns.  Our declarative programming model
  called \name\ treats replication as a form of versioning, in which
  consistency is enforced through programmer-supplied \emph{merge}
  functions.  Distributed state is now viewed in terms of a tree of
  immutable object versions, with merge actions used explicitly by the
  application or implicitly by the underlying runtime system to
  periodically reconcile local versions to yield a consistent global
  state.  Our model frees the programmer from having to think of
  low-level operational notions related to distribution and
  replication, and therefore does not entail any restructuring of
  application logic to enable distributed programming.

>>>>

  In this paper, we present a new interpretation of replicated types
  that overcome these concerns.  Our declarative programming model
  called \name\ treats replication as a compositional form of
  versioning, in which consistency is enforced through
  programmer-supplied \emph{merge} functions.  Distributed state is
  now viewed in terms of a tree of immutable object versions, with
  merge actions used explicitly by the application or implicitly by
  the underlying runtime system to periodically reconcile local
  versions to yield a consistent global state.  Our model frees the
  programmer from having to think of low-level operational notions
  related to distribution and replication, and therefore does not
  entail any restructuring of application logic to enable distributed
  programming.

### 2017-02-27 paper/related.tex
edits

Our idea of versioning state bears resemblance to Concurrent
Revisions~\cite{BBL+10}, a programming abstraction that provides
deterministic concurrent execution by forking and merging
\emph{versions}, portions of state shared among concurrent threads.
The idea of using revisions as a means to programming eventually
consistent distributed systems was further developed
in~\cite{BFL+12,Burckhardt2012}.  The \name\ programming model,
however, differs substantially from a concurrent revisions model
because it imposes no distinction between \emph{servers}, machines
that hold global state, and \emph{clients}, devices that operate on
local, potentially stale, data - any computation executing in a
distributed environment is free to fork new versions, and synchronize
against other replicated state.  Our model, furthermore, supports
fully decentralized operation and is robust to network partitions and
failures. Just as significantly, \name\ allows applications to
customize join semantics with programmable merge operations.  Indeed,
the integration of a version-based mechanism within OCaml allows a
degree of type safety, composability, and polymorphism not available
in related systems.

>>>>

Our idea of versioning state bears resemblance to Concurrent
Revisions~\cite{BBL+10}, a programming abstraction that provides
deterministic concurrent execution by forking and merging
\emph{versions}, portions of state shared among concurrent threads.
The idea of using revisions as a means to programming eventually
consistent distributed systems was further developed
in~\cite{BFL+12,Burckhardt2012}.  The \name\ programming model,
however, differs substantially from a concurrent revisions model
because it imposes no distinction between \emph{servers}, machines
that hold global state, and \emph{clients}, devices that operate on
local, potentially stale, data - any computation executing in a
distributed environment is free to fork new versions, and synchronize
against other replicated state.  Our model, furthermore, supports
fully decentralized operation and is robust to network partitions and
failures. Just as significantly, \name\ allows applications to
customize join semantics with programmable merge operations.  Indeed,
the integration of a version-based mechanism within OCaml allows a
degree of type safety, composability, and profitable use of
polymorphism not available in related systems.
